\begin{abstract}
Resource management (RM) software is crucial to HPC
for efficient application execution on a set of diverse, large resources.
%
However, growing numbers and types of compute resources
and a greater interplay among various resources 
(e.g., between compute clusters and a shared I/O cluster) 
across the entire HPC center can render even 
the best-in-breed RM software increasingly ineffective.
HPC centers are at a junction where they require
a major shift in the conceptual model of resource management
in order to meet the challenges of extreme scalability,
a diversity of resources, and challenges such as power budgets.

Our response to this critical need is \flux, a RM software
framework that can solve the key RM challenges
in a simple, extensible, distributed, and autonomous fashion.
It aims to manage the entire computing facility as one common pool
of diverse sets of resources to provide
efficient scheduling decisions and easy accommodation
of site-wide constraints.

Further, \flux\ employs a framework approach to facilitate 
the seamless integration of system monitoring and administration,
lightweight virtualization, and parallel programming and tools
run-time systems.
We discuss \flux's vision, design challenges,
and concepts, and then report our progress prototyping
key components.
Our preliminary results show that the run-time  
provides requisite properties such as high scalability
and easy integration and interoperability among essential
run-time elements such as MPI, run-time tools and middleware.
\end{abstract}
