\section{Conceptual design of \flux}
\label{models}
Flux is the open-source RJMS framework we are actively
investigating to embody the new paradigm while
addressing the multitude of challenges described above.
This section describes some of its fundamental design
concepts.

\vspace{1ex}
\noindent{\em Unified Job Model: } In the traditional paradigm, 
a job is simply defined to be a resource allocation. 
But \flux\ unifies this notion with an independent 
RJMS instance. Because any \flux\ job has 
an independent resource and job management services,
it can recursively accept and schedule jobs and provide its own 
services to them. 
The RJMS instance must be delegated
the main responsibility of managing the resources allocated
to its job. But it must allow specialized service
plug-ins to be instantiated so that these resources
can be used differently than other resources.  
This model forms 
the foundation for a hierarchical,
multilevel resource management and job scheduling
with resource subset specialization.

\vspace{1ex}
\noindent{\em Job Hierarchy Model:} To scale the new paradigm 
to the entire HPC center, we must avoid a centralized approach. 
Instead, \flux\ employs a hierarchical resource management 
and job scheduling by forming a tree-based hierarchy of \flux\ jobs. 
Several guiding principles throughout the job hierarchy strike 
a balance between the management responsibility 
of a parent job and delegation and empowerment of a child job:

\begin{itemize}
\item{Parent bounding rule: the parent job grants 
and confines the resource allocation of all of its children.}

\item{Child empowerment rule: within the bound set 
by the parent, the child job is delegated the ownership 
of the allocation and becomes solely responsible 
for most efficient uses of the resources.}

\item{Parental consent rule: the child job asks 
its parent when it wants to grow or shrink the resource 
allocation, and it is up to the parent to grant the request.}
\end{itemize}

This model has many advantages for scalability of both
resource management and job scheduling. 
The independent and specialized \flux\ service instance
of a job becomes only responsible for managing its direct
child jobs, which would be only a small fraction of
the total number of jobs at the center. 
As sibling jobs run simultaneously, their independent
\flux\ instances will perform concurrent management services.

For example, for job scheduling, this model enables \flux\
to exploit scheduling parallelism~\cite{Omega,Mesos}.
A parent scheduler schedules at coarse granularity 
over a large collection of resources and leases different resource subsets 
to its children schedulers. 
At the same time, this will enable Flux to specialize the scheduling behaviors 
on subsets of resources without having to introduce a
complex global scheduling policy into the centralized, monolithic scheduler. 

In short, this model enforces the first principle 
of the new paradigm: imposing highly complex resource bounds 
to provide high operational efficiency 
at any level across the entire center, while enabling 
most efficient execution and scheduling of the workloads 
within these bounds. 
Further, this addresses 
many of the identified challenges in Section~\ref{label:paradigm} 
including the {\em multidimensional scale} and 
{\em diverse/dynamic workload} challenges. 

%\vspace{1ex}
\noindent{\em Generalized Resource Model:} In the traditional 
paradigm, compute resources are modeled primarily 
as a collection of compute nodes. But this is a simplistic perspective 
ill-suited for the new paradigm. Today's applications 
are diverse with disparate limiting performance factors 
beyond floating point computation. 
Further, computing centers are increasingly concerned 
about managing new resource types such as power 
and shared persistent storage. Our generalized resource
model addresses this need by providing an extensible
and flexible representation for resources
and their relationships.

%\vspace{1ex}
\noindent{\em Multilevel Resource Elasticity Model:} As our 
applications and their programming models are becoming 
increasingly dynamic, the new paradigm demands 
an elasticity model where an existing resource allocation 
can grow and shrink, depending on the current needs 
of applications and/or the HPC center. 
\flux\ supports the elasticity model within our job hierarchy 
framework above: a child job sends a grow or shrink request 
to its parent, which can go up the job hierarchy 
until all requisite constraints are known for this request. 
Also, combining this with the generalized resource model, 
the elasticity can be expressed for various resource including 
power consumption. Our elasticity model addresses 
the {\em dynamic workload} challenge.

%\vspace{1ex}
\noindent{\em Common Scalable Communication Infrastructure Model:} 
Our scalability strategy with respect to a large number 
of compute nodes is to provide a common scalable communication 
framework within each job. When a job is created, a secure, scalable 
overlay network with common communication service is established 
across its allocated nodes. Except for the root-level job, 
the existing communication session of the parent job assists 
the child job with rapid creation of its own session. 

A communication session is only aware of its parent 
and child and passes the limited set of control information 
through its communication channel. Thus, this model 
enables highly scalable communication within a job, while 
limiting communications between jobs, addressing 
both the {\em multidimensional scale} as well as security issues.
Further, this backbone per-job communication network 
supports well-known bootstrap interfaces 
for distributed programs including many MPI implementations 
as well as run-time tools. This provides tightly integrated support
for the development and use of scalable run-time tools, which 
can have a large impact on user productivity.
